---
title: 'Assignment #1 - PALMA'
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_download: true
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)         # for graphing and data cleaning
theme_set(theme_minimal()) # Lisa's favorite theme
```

```{r data}
# Read in data here
```

-   Below, post a link to your GitHub repository - the main page which should show the README is fine.

https://github.com/apalma127/assignment-1


## Creating a website

DONE

**Tasks**:


-   Include a link to your website below.

https://anthonypalma.netlify.app/


-   Listen to at least the first 20 minutes of "Building a Career in Data Science, Chapter 4: Building a Portfolio". Go to the main [podcast website](https://podcast.bestbook.cool/) and navigate to a podcast provider that works for you to find that specific episode. Write 2-3 sentences reflecting on what they discussed and why creating a website might be helpful for you.

## Project ideas

Answer the following questions to start thinking about the project.

-   What are some topics (or a single topic) you are interested in studying from a data science perspective? These can be very specific or more general.  

-   Given your to topic(s), where would you find data about it? Provide at least two sources, being as specific as possible. If you need to collect/scrape it yourself, describe the steps you'd need too take.

-   What challenges do you imagine having? How might you overcome them?  

-   Respond to the Project Survey on moodle.

## Bias and Fairness

Listen to Dr. Rachel Thomas's [Bias and Fairness lecture](https://ethics.fast.ai/videos/?lesson=2). Write a brief paragraph reflecting on it. You might also be interested in reading the [ProPublica article](https://www.propublica.org/article/machine-bias-risk-assessments-in-criminal-sentencing) Dr. Thomas references about using a tool called COMPAS to predict recidivism. Some questions/ideas you might keep in mind:

-   Did you hear anything that surprised you?

-   Why is it important that we pay attention to bias and fairness when studying data science?

-   Is there a type of bias Dr. Thomas discussed that was new to you? Can you think about places you have seen these types of biases?
